Tina Paper In Development

### 2024-10-07 docs/writing/paper.tex
Adding some about automatic control

\subsubsection{Image Stack Focusing}
When the sample is placed on the table to be digitized, it is assumed that there will, at best, very slight variations in height across the surface area of the sample. A levelling table 
assists in reducing this error although it will never be nonzero. At each location (X, Y) on the grid of overlapping images, 11 images are captured in equally distanced Z steps across a 1mm range. 
Each of these images have a normalized variance score calculated - the maximum value represents the most in focus image \citep{sampat_extensive_2014}.

\subsubsection{Automatic Control}

@@

>>>>

\subsubsection{Image Stack Focusing}
When the sample is placed on the table to be digitized, it is assumed that there will, at best, very slight variations in height across the surface area of the sample. A levelling table 
assists in reducing this error although it will never be nonzero. At each location (X, Y) on the grid of overlapping images, 11 images are captured in equally distanced Z steps across a 1mm range. 
Each of these images have a normalized variance score calculated - the maximum value represents the most in focus image \citep{sampat_extensive_2014}. In practice, stopping and starting the motor causes 
enough vibration to require upwards to two seconds of pause time before the motion blur stops to take each photo. Instead of stopping and starting each image, an additional distance is added to the 
Z-motion to allow the stepper to accelerate and reach constant velocity. At this speed, images are then taken with constant time steps instead of constant distance steps across the 1mm range. This eliminates
the motion blur due to acceleration and dramatically reduces imaging time.

@@

\subsubsection{Automatic Control}
While the image stack provides a basis to obtain an in focus image, it is statically limited to the 1mm range in Z-values. Instead of spending significant time guaranteeing that the sample
is within the Z-value range across the entire surface area, a PID control algorithm takes the wheel. The information previously calculated in the image stack is sufficient 
to inform the PID controller of how to adjust the initial Z-value for the next image stack. The controller is constantly trying to make the most in focus image be at the center of the image stack,
index value 5. This allows for the most flexibility moving to the next location of the image grid.
